### 2021-06-03 paper/calibration_and_estimation.tex
Update the work multiplier figure and add figure on the share of individuals with rapid tests.

\begin{figure}[ht]
    \centering
    \includegraphics[width=1.1 \textwidth]{../figures/results/figures/work_multiplier_since_sep}
    \caption{Share of Workers with Work Contacts}
    \label{fig:work_multiplier}
    \figurenotes{The figure shows the work mobility as reported by \cite{Google2021}. We take this as a proxy of the share of workers who are not in home office, i.e. who still have physical work contacts.}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \caption{Share of Individuals Having Ever Done a Rapid Test}
    \label{fig:share_ever_rapid_test}
    \begin{subfigure}{.6\textwidth}
      \includegraphics[width=0.9 \textwidth]{../figures/results/figures/scenario_comparisons/spring_fit/full_share_ever_rapid_test}
    \end{subfigure}%
    \begin{subfigure}{.6\textwidth}
      \includegraphics[width=0.9 \textwidth]{../figures/results/figures/scenario_comparisons/spring_fit/full_share_rapid_test_in_last_week}
    \end{subfigure}
    \caption{Share of Individuals Having Done a Rapid Test in the Last Week}
    \label{fig:explain_decline}
    \figurenotes{\textcolor{red}{\ldots}}
\end{figure}

>>>>

\begin{figure}[ht]
    \centering
    \includegraphics[width=1.1 \textwidth]{../figures/results/figures/data/work_multiplier_since_sep}
    \caption{Share of Workers with Work Contacts}
    \label{fig:work_multiplier}
    \figurenotes{The figure shows the work mobility as reported by \cite{Google2021}. We take this as a proxy of the share of workers who are not in home office, i.e. who still have physical work contacts.}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \caption{Share of Individuals With Rapid Tests}
    \label{fig:share_ever_rapid_test}
    \begin{subfigure}{.6\textwidth}
      \includegraphics[width=0.9 \textwidth]{../figures/results/figures/scenario_comparisons/spring_fit/full_share_ever_rapid_test}
    \end{subfigure}%
    \begin{subfigure}{.6\textwidth}
      \includegraphics[width=0.9 \textwidth]{../figures/results/figures/scenario_comparisons/spring_fit/full_share_rapid_test_in_last_week}
    \end{subfigure}
    \caption{Share of Individuals Having Done a Rapid Test in the Last Week}
    \label{fig:share_rapid_test_last_week}
    \figurenotes{The figure compares the share of individuals who have ever done a rapid test or done a rapid test within the last week in our simulations to the shares reported in the \href{https://projekte.uni-erfurt.de/cosmo2020/web/topic/wissen-verhalten/80-schnelltests/}{COVID-19 Snapshot Monitoring survey}. The
    left panel compares the share of individuals who have ever done a rapid test. The right panel compares the share of individuals who have done a rapid test within the last seven days in our simulation compared to the share reporting to have done at least weekly rapid tests in the last four weeks in the COSMO survey. Overall our calibration of rapid tests are slightly conservative. The overall share is below that in the study. We fit the share of weekly tests quite exactly. However, the study only covers adults while our share also includes children who are tested very regularly when attending school.
    }
\end{figure}
